---
title: "halfsib_fecundity"
author: "Enoch Ng'oma"
date: "3/26/2018"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

# Function to calculate the mean and the standard deviation for each group
  
```{r}
# data : a data frame
# varname : name of column to be summarized
# groupnames : vector of grouping variables

data_summary <- function(data, varname, groupnames){
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum <- data %>%
    group_by(groupnames) %>% 
    summarize(summary_func(., varname))
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}
```

# packages

```{r}
library(tidyverse) 
library(cowplot)
```

# data

```{r}
h2fec_phenotype <- read.table('../../Data/Processed/eggs_per_vial.txt',
                     sep = "\t", header = TRUE,
                     stringsAsFactors = FALSE)

h2fec_phenotype <- as_tibble(h2fec_phenotype)
h2fec_phenotype <- dplyr::rename(h2fec_phenotype, Diet = treat)
```

# change LY to DR, STD to C
```{r}
h2fec_phenotype <- h2fec_phenotype %>%
     mutate(Diet=replace(Diet, Diet=="LY", "DR")) %>%
     mutate(Diet=replace(Diet, Diet=="STD", "C"))

```

##### density (ggplot)

```{r, dens}
#pdf("../../Data/Figures/density_all-data_ggpl.pdf",width=6,height=4)
par(mar=c(4.5,4.5,0.5,0.5))
 ggplot(h2fec_phenotype, aes(egg_total, fill = Diet)) + 
  geom_density(alpha = 0.8) +
  #coord_cartesian(xlim=c(0, 1e4), ylim=c(0, 5e4)) + #adjust frame of x-axis
  scale_x_continuous(expand=c(0, 0), limits=c(0, 5.5e2)) + #limit plot area on x-axix
  scale_color_manual(values=c("#CC6666", "#9999CC", "#66CC99")) +
  theme(axis.title = element_text(face="bold", size=16)) +
  xlab("Lifetime fecundity") + ylab("Density") +
  theme(legend.position=c(0.1, 0.9)) +
  scale_fill_discrete(name="Diet", labels=c("HS", "DR", "C")) 
#dev.off()
```

# summarize data

```{r}
# h2fec_sum <- data_summary(h2fec_phenotype, varname="egg_total",
#                     #groupnames=c("supp", "dose")) # if have multiple grouping variables
#                     groupnames="Diet")

h2fec_sum <- h2fec_phenotype %>% 
  group_by(Diet) %>% 
  summarise(egg_total_mean = mean(egg_total, na.rm = TRUE),
            sd = sd(egg_total)) %>% 
  rename(egg_total = egg_total_mean)

# Convert dose to a factor variable
h2fec_sum
```


# Diet groups and error bars

```{r}
# Standard deviation of the mean as error bar
p <- ggplot(h2fec_sum, aes(x=Diet, y=egg_total, fill=Diet)) + 
    geom_bar(stat="identity", position=position_dodge(), width=0.9) +
    geom_errorbar(aes(ymin=egg_total-sd, ymax=egg_total+sd), width=.2,
                  position=position_dodge(.9)) +
    scale_y_continuous(expand = c(0,0))
  
p + scale_fill_grey() + theme_minimal()

p + labs(title="Lifetime eggs per diet treatment", 
         x="Diet", y = "Eggs per female")+
    scale_fill_grey(guide=FALSE) + 
   #scale_fill_manual(values=c('black','lightgray'))+ # Change color by groups
   theme_classic()

# change plot size

```
# optional formatting
#p + scale_fill_brewer(palette="Paired") + theme_minimal() #paired bars
#p + scale_fill_manual(values=c('black','lightgray'))  #great black $ grey theme
#p + scale_fill_brewer(palette="Greens") + theme_minimal() #great greens
#p + scale_fill_brewer(palette="Reds") + theme_minimal() #great reds

```{r}
#dot plot

k6 <- ggplot(data=h2fec_phenotype, aes(x=Diet, y=egg_total, fill=Diet)) + #group-sire_trt
  #geom_point(pch=21) +
  geom_jitter(position = position_jitter(width = 0.4), alpha = 0.7)+
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  scale_y_continuous(expand = c(0,0)) +
  xlab("Diet") + ylab("Total eggs") 
k6 +   expand_limits(y = c(1, 5e2)) 

t <- subset(h2fec_phenotype, h2fec_phenotype$Diet=="HS")
which.max(t$egg_total)
t[68,] # S45D134_a_HS has egg_total = 404
# problem image is IMG_5571.JPG set 2016-03-05 flip 2016-05-24 age 80, 2 females, 48.5 eggs per female

kn <- h2fec_phenotype

``` 


```{r}
# new grouping variable
h2fec_phenotype <- unite(h2fec_phenotype, "sire_Diet", sireid, Diet, sep = "_", remove=FALSE)  

#h2fec_phenotype <- select(h2fec_phenotype, sire_Diet, Diet, egg_total)

```

```{r}

#with(h2fec_phenotype, reorder(sire_Diet, egg_total)) 
#pdf("../../Data/Figures/fecundity_family.pdf",width=6,height=4)
par(mar=c(4.5,4.5,0.5,0.5))

#ascending order
p <- ggplot(h2fec_phenotype, aes(x= reorder(sire_Diet, egg_total), y=egg_total, fill=Diet)) +

#descending order
#ggplot(h2fec_phenotype, aes(x= reorder(sire_Diet, -egg_total), y=egg_total, fill=Diet)) + 
  
  theme(axis.text.x = element_blank(), legend.position = 'top') +
    stat_summary(fun.y = mean,
               position = position_dodge(width = 0.9),
               geom = "bar", alpha=0.8) +
  xlab("Sire family") + ylab("Total eggs") +
  scale_y_continuous(expand = c(0,0))+
  #scale_fill_discrete(name="Diet")+
  #guides(fill=guide_legend(title="Diet")) +
geom_point(aes(color=Diet), position = position_dodge(width = 0.9),size=0.75) 

p +   expand_limits(y = c(1, 5e2)) 
#tt + guides(fill=guide_legend(title="Diet"))

#dev.off()
```


# reaction norms for sire families

```{r}
# prep each treatment into its own column

#pull HS and compute median
HS <- subset(h2fec_phenotype, Diet == "HS")
hs_trim <- cbind.data.frame(HS$sireid, HS$egg_total)
hs_med <- aggregate(. ~ HS$sireid, data=hs_trim, FUN=median)
hs_med[,2] <- NULL
colnames(hs_med) <- c("sireid","eggs")
hs_med$diet<-"HS"

#pull LY and compute median
DR <- subset(h2fec_phenotype, Diet == "DR")
dr_trim <- cbind.data.frame(DR$sireid, DR$egg_total)
dr_med <- aggregate(. ~ DR$sireid, data=dr_trim, FUN=median)
dr_med[,2] <- NULL
colnames(dr_med) <- c("sireid","eggs")
dr_med$diet<-"DR"

#pull STD and compute median
C <- subset(h2fec_phenotype, Diet == "C")
c_trim <- cbind.data.frame(C$sireid, C$egg_total)
c_med <- aggregate(. ~ C$sireid, data=c_trim, FUN=median)
c_med[,2] <- NULL
colnames(c_med) <- c("sireid","eggs")
c_med$diet<-"C"
```

# join data frames

```{r}
B <- rbind(hs_med, c_med, dr_med)
#B<-B[!(B$sireid=="S39"),]
#attach a column of diet to each data frame before joining; use that as fill

#reorder x-axis (ggplot default is alphabetical)
B$diet <- as.character(B$diet) #turn diet col into a char vector
B$diet <- factor(B$diet, levels=unique(B$diet)) #back to ordered factor
#save(B, file = "/Users/ngomae/Documents/H2_Analysis/h2lifespan/Evo17_Portland/h2reacts.Rda")
```

# plot reaction norms for sire families

```{r}
#pdf("../../Data/Figures/h2life_reaction_norms.pdf",width=6,height=4)
par(mar=c(4.5,4.5,0.5,0.5))
ggplot(B, aes(x = B$diet, y = B$eggs)) +
  geom_point(size = 2)+
  geom_line(aes(group = paste(sireid), alpha = 0.2)) +
  xlab("Dietary condition") + ylab("Total eggs") +
  theme(legend.position="none") +
  scale_fill_discrete(name="Diet", labels=c("HS", "DR", "C"))
  
  #expand_limits(x = "diet") + scale_x_continuous(expand = c(0, 0))
  #expand_limits(x = 0, y = 0)
  #expand_limits(y = c(0, 4.5e2))
  

#dev.off()
```


# per week analysis

```{r}
AA <- read.table('../../Data/Processed/eggs_per_female.txt',
                     sep = "\t", header = TRUE,
                     stringsAsFactors = FALSE)

AA <- AA %>%
   select(flipDate,id,fID,treat,age,sireid,damid,n_females,eggs_per_female)
#AA
AA <- as_tibble(AA)
```

```{r}
AA <- AA %>%
  rename(Diet = treat) %>%
  mutate(Diet=replace(Diet, Diet=="LY", "DR")) %>%
  mutate(Diet=replace(Diet, Diet=="STD", "C"))
#AA
```


```{r}
AA$flipDate <- as.Date(AA$flipDate)

AA <- AA[!is.na(AA$eggs_per_female), ]

A1 <- aggregate(AA["eggs_per_female"], by=AA["flipDate"], sum)

# a new grouping variable
AA <- unite(AA, "sire_trt", sireid, Diet, sep = "_", remove=FALSE)
A2 <- aggregate(AA["eggs_per_female"], by=AA["sire_trt"], sum)

```

# Julian dates

```{r}
#head(AA)

AB <- as.data.frame(AA)
AB$flipDate <- as.Date(AB$flipDate)

AB$julian_date <- julian(AB$flipDate)
#head(AB)

# sort by julian date
AB <- AB[order(AB$julian_date),] 

AB.c <- transform(AB, Time_Week=match(julian_date, unique(julian_date)))
all.equal(AB,AB.c)

```


```{r}

A3 <- AB.c %>%
   select(Time_Week,age, Diet,eggs_per_female)

A3$Diet <- as.character(AA$Diet)

A3 <- aggregate(.~Time_Week+Diet, A3, mean)

k <- ggplot(A3, aes(x=Time_Week, y=eggs_per_female))+
  geom_line(aes(color=Diet)) +
  xlab("Age (days))") + ylab("Mean eggs/female/day")
#k

k1 <- ggplot(A3, aes(x=Time_Week, y=eggs_per_female, color=Diet))+
  geom_point(aes(shape=Diet))+
  xlab("Age (days))") + ylab("Mean eggs/female/day")

# local polynomial regression
k1 + geom_smooth(method="loess") #try "lm"

# facet

k2 <- ggplot(A3, aes(x=age, y=eggs_per_female, color=Diet))+
  geom_point(aes(shape=Diet)) +  geom_smooth(method="loess") +
  xlab("Age(days") + ylab("Mean eggs/female/day")
k2 + facet_grid(. ~ Diet)#facet_grid(Diet~ .) 


k3 <- ggplot(A3, aes(x=age, y=eggs_per_female, color=Diet))+
  geom_point(aes(shape=Diet)) +  geom_smooth(method="loess")+
  xlab("Age (days)") + ylab("Mean eggs/female/day")
k3 + facet_grid(Diet~ .) 

```


```{r}
#pdf("../../Figures/h2_avg_fecundity_per_female_per_day.pdf",width=6,height=4)
par(mar=c(4.5,8.0,0.5,0.5))

lml <- ggplot(data=AB.c, aes(x=age, y=eggs_per_female, fill=Diet)) +
geom_point(pch=21) +
#geom_smooth(span=0.8)+
geom_jitter(position = position_jitter(width = .4), alpha = 0.07) +
scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
xlab("Age (days)") + ylab("Mean eggs/female/day") +
scale_y_continuous(limits = c(0,100), expand = c(0, 0)) +
geom_smooth(method = "lm", se = TRUE, color="black")+
facet_grid(.~Diet)
lml
#dev.off()
```







