---
title: "h2 fecundity analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(cowplot)
library(readxl)
```

## Regression on handcounted images

```{r}
linear_threshold <- 46

# Load data for handcounts
HC <- suppressWarnings(
  read_excel("../../Data/Processed/hd_hand_counted.xlsx") %>% 
  dplyr::select(camera_id, handcount)
)

# Load list of bad images that were handcounted
bad_images <- read_excel("../../Data/Processed/bad_images.xlsx") %>% 
  filter(status == "bad") %>% 
  rename(camera_id = cameraid)

# Drop bad images
HC <- HC %>%
  filter(!(camera_id %in% bad_images$camera_id))

linear_area <- read_csv("../../Data/Processed/area_summation_HC_linear_fine.csv",
                       col_types = "cii") %>% 
  filter(lower_thresh == linear_threshold) %>% 
  dplyr::select(-lower_thresh) %>% 
  rename(area_linear = area)

# Join handcounts with areas
HC <- inner_join(HC, linear_area) %>% 
  as.data.frame()
```

Check these areas: should be in the test_case batch but aren't.

```{r}
HC %>% 
  filter(is.na(area_linear))
```

## Examine possibly bad images

```{r check_bad_images, cache = FALSE}
plot_jpeg = function(path, add=FALSE) {
  # https://stackoverflow.com/a/28729601/168137
  require('jpeg')
  jpg = readJPEG(path, native = TRUE) # read the file
  res = dim(jpg)[2:1] # get the resolution, [x, y]
  if (!add) # initialize an empty plot area if add==FALSE
    plot(1, 1,
         xlim = c(1, res[1]), ylim = c(1, res[2]),
         asp = 1, type = 'n', xaxs = 'i',
         yaxs = 'i', xaxt = 'n', yaxt = 'n',
         xlab = '', ylab = '', bty = 'n', main = path)
  rasterImage(jpg, 1, 1, res[1], res[2])
}

flagged_images <- HC %>% 
  filter(area_linear > 2.5e05)

basedir <- "../../../h2_fec_images/h2_thresh_images/"

if (nrow(flagged_images) >= 1) {
  for (ii in 1:nrow(flagged_images)) {
    print(plot_jpeg(paste0(basedir, flagged_images$camera_id[ii])))
  }
}
```

## Prediction for all images

Linear model predicting egg count from area:

```{r fm_linear, results="hide", cache=TRUE, warning=FALSE}
fm_lm <- lm(handcount ~ area_linear - 1, data = HC)
```

```{r}
new_data <- tibble(
  area_linear = seq(0, 1.25 * max(c(HC$area_linear)),
                    length.out = 200))

new_data$lm_pred <- predict(fm_lm, newdata = new_data)

ggplot() +
  geom_line(data = new_data, aes(x = area_linear, y = lm_pred)) +
  geom_point(data = HC, aes(x = area_linear, y = handcount))
```

## Evaluation of linear model

```{r cache = TRUE}
HC$lm_pred <- predict(fm_lm)

cor(HC$handcount, HC$lm_pred)
```

## Predict for new data

```{r cache=TRUE}
suppressWarnings(
  M <- read_excel("../../Data/Processed/feclife_with-image-ids.xlsx")
)

# Load areas
h2_fec_areas <- read_csv("../../Data/Processed/area_summation_linear_h2_fecimages.csv",
                         col_types = "cii")

M <- left_join(M, h2_fec_areas) %>% 
  rename(area_linear = area) %>% 
    drop_na(area_linear)

M$predicted_count_linear <- predict(fm_lm, newdata = M)
```

## Checks

Check these. They are handcounted but in the set of analyzed images.

```{r}
M %>% 
  filter(is.na(test_case)) %>% 
  filter(!is.na(handcount)) %>% 
  filter(handcount != "unassessable") %>% 
  filter(handcount != "unassigned") %>% 
  mutate(handcount = as.numeric(handcount)) %>% 
  select(camera_id, handcount, predicted_count_linear) %>% 
  filter(!is.na(predicted_count_linear))
```

## Some exploration

```{r}
ggplot(M, aes(predicted_count_linear)) +
  geom_histogram(bins = 30)
```

Check high and low predicted eggs

```{r}
M %>% 
  select(camera_id, predicted_count_linear) %>% 
  arrange(desc(predicted_count_linear))
```

```{r}
M %>% 
  select(camera_id, predicted_count_linear) %>% 
  arrange(predicted_count_linear)
```

```{r}
M.low <- M %>% 
 select(camera_id, predicted_count_linear) %>% 
 arrange(predicted_count_linear)

M.low <- M.low[1:300,]

ee <- read_excel("../../Data/Processed/egg_notes_EGK.xlsx")
ee$Image <- paste("IMG_", ee$Image, ".JPG", sep = "")
ww <- which(M.low$camera_id %in% ee$Image)

M.low <- M.low[-ww,]

set.seed <- 8462
set.zeros <- M.low[sample(seq(1, nrow(M.low)), 10) , ]
```

## Examine possibly bad images

```{r check_bad_images_2, eval = TRUE}
plot_jpeg = function(path, add=FALSE) {
  # https://stackoverflow.com/a/28729601/168137
  require('jpeg')
  jpg = readJPEG(path, native = TRUE) # read the file
  res = dim(jpg)[2:1] # get the resolution, [x, y]
  if (!add) # initialize an empty plot area if add==FALSE
    plot(1, 1,
         xlim = c(1, res[1]), ylim = c(1, res[2]),
         asp = 1, type = 'n', xaxs = 'i',
         yaxs = 'i', xaxt = 'n', yaxt = 'n',
         xlab = '', ylab = '', bty = 'n', main = path)
  rasterImage(jpg, 1, 1, res[1], res[2])
}

flagged_images <- M %>% 
  filter(predicted_count_linear > 2000)

basedir <- "../../../h2_fec_images/h2_thresh_images/"

if (nrow(flagged_images) >= 1) {
  for (ii in 1:nrow(flagged_images)) {
    print(plot_jpeg(paste0(basedir, flagged_images$camera_id[ii])))
  }
}
```

